\chapter{Trusted Platform Module}
The Trusted Platform Module is a system component used as a cryptographic co-processor. It was developed by and standardized by the Trusted Computing Group (TCG) consortium to lay a foundation on which secure systems could be further created and developed. 

\section{Basic concepts}
This section provides an overview of basic concepts mentioned trough in this work.

\subsection{Platform Configuration Registers}
Platform Configuration Registers (PCRs) are dynamic memory locations inside a TPM used to store integrity metrics of software and its configuration. These locations can only be updated using \texttt{extend} operation and also read for reporting or attestation. The \texttt{extend} operation makes use of the cryptographic hash function to combine the digest stored in the PCR and the new data. Cryptographic hash function map data of arbitrary size to the output of a fixed size. Such outputs are conventionally called hashes, message digests, or digests. These functions have one-way property: when given a message digest, it is difficult  to compute the message itself. The extend operation works in the following way:
\begin{align*}
    d_{n+1} = h(d_{n}\ ||\ data)
\end{align*}
\begin{itemize}
    \item $||$ is a concatenation of data in binary form
    \item $ d_{n} $ is a digest stored in PCR before \texttt{extend} operation
    \item $ d_{n+1} $ is a digest stored in PCR after \texttt{extend} operation
    \item $ data $ is binary data to extend by
    \item $ h $ is a cryptographic hash function
\end{itemize}

We can always recompute the final value if we possess the knowledge of members previously used in the chain and detect potential alterations made to the set measurements reported by the system. 



\section{History}
The first broadly used specification was TPM 1.1b, released in 2003. TPMs released under this specification already provided some essential functions found in modern TPMs consisting of key generation of RSA key pairs, storage, secure authorization, and device-health attestation. Anonymous identity keys based on certificates were used in order to assure privacy. However, the certificates needed to be provided with the TPM, and any generation of such keys was available only upon owner authorization. To prove the origin of the keys generated by TPM anonymously, a privacy certification authority was created. PCRs provide the integrity of measurements collected during the system's boot sequence. Both PCRs and identity keys might be used to prove the health of the system's boot sequence~\cite[p.~2]{arthur2015practical}.

The hardware specification was not standardized in TPM 1.1b. This caused various incompatibilities. The TPMs across different vendors provided differing interfaces, which required different drivers. Pin-outs on the chips were not prescribed by any standard. Additionally, there were no countermeasures against dictionary attacks~\cite[p.~2]{arthur2015practical}.
% Should i also mention DAA ?

While being in development from 2005 to 2009, the TPM 1.2 specification went through numerous releases. Regarding the need to store shipped certificates for TPM's endorsement keys on a hard disk, about 2KB of non-volatile RAM was added. A new design needed to be made to support key migration between different TPMs because the old design of key migration would in TPM 1.12 require users to have TPM owner authorization. The new idea enabled users to create migratable keys and then relied on a designated third party that could exclusively migrate such keys. Said keys could also be certified. Thus, they were called Certified Migratable keys. An internal timer able to synchronize with the external one was added in 1.12, which has its use when signing data due to timestamps. Version 1.12 required API to provide backward compatibility for 1.1b. This increased the complexity of the new specification. The TPM 1.12 became widely used in x86 personal computers starting 2005 and later in 2008 also in servers~\cite[p.~3]{arthur2015practical}.

One factor contributing to the need for yet another specification after TPM 1.12 was that in 2005, some substantial collision attacks were found against the SHA-1 hash function. Analysis regarding the use of SHA-1 in TPM revealed the attacks not being applicable~\cite{tcg_tpm1.12_sha-1_uses}. Due to the extensive use of SHA-1 in TPM 1.12, the new specification had to permit any hashing algorithm without making any changes to the specification. A so-called \texttt{digest agility}. Another problem was the lack of a symmetric algorithm required in the TPM specification. The use of RSA for encryption of serialized data was impractical because RSA operations are slow. Neither would help support bigger-sized RSA keys because that would cause a higher chip cost, incompatibility issues, and lower performance. That's why it was decided that the following specification would adopt support for symmetric encryption, which is faster and more suitable for encryption of large byte streams. Having this many problems, an overhaul of the specification would be convenient. And the architects of TPM 2.0 took advantage of the situation~\cite[p.~4]{arthur2015practical}.

\section{TPM 2.0}
%First sentence is prob a nonsense
The main goal of the new specification was to provide a library describing features and commands available for implementation. This architecture allows designers to choose the required level of security, which may vary for different use cases. 

\subsection{Types}
There is no single correct way how should TPM 2.0 be implemented. Different usage scenarios may require a different type of TPM. They may come in different shapes assuming they are hardware-based, may be integrated into another chip, or may be implemented in software. According to \cite{tcg_tpm2_briefintro}, there are five main types of a TPM.

\begin{itemize}
    \item \textbf{Discrete TPM} is a hardware implementation of TPM specification. It is implemented as a standalone chip designed to be highly secure and tamper-proof and used to protect even against very advanced attacks in security-critical infrastructures.
    \item \textbf{Integrated TPM} is still implemented in hardware, although as a part of a more complex chip, such as CPU, which may have other responsibilities than security. They are not required to be tamper-resistant because such a requirement may immensely increase such chips' cost.
    \item \textbf{Firmware TPM} runs in the CPU's trusted execution environment (TEE), which protects and isolates the code and data along with providing confidentiality and integrity guarantees. Firmware TPM's security is very dependent on the TEE's security.
    \item \textbf{Software TPM} is implemented as an emulator ideally used for testing and system prototyping purposes due to its weak security.
    \item \textbf{Virtual TPM} does not require a physical chip to be present. It  entirely relies on the fact, its users will be hypervisors, and the Virtual TPM itself will be isolated from the software running on the virtual machine to protect its code. Virtual TPMs may provide the same level of security as discrete TPMs.
\end{itemize}


\subsection{Functionality}


\section{Performance analysis}
\subsection{tpm2-algtest}
The \texttt{tpm2-algtest}\footnote{https://github.com/crocs-muni/tpm2-algtest} is a tool for automatic gathering of information about the TPM2 devices \cite{Struk2019thesis}. The tool uses libraries implementing Trusted Computing Group's TPM2 Software Stack\footnote{https://github.com/tpm2-software/tpm2-tss} which allows for simplification of development when programming applications supposed to interact with the TPM. The tool tests for support of specific commands and supporting routines, values of structures defined in the TPM 2.0 specification \cite{tcg_p3_commands, tcg_p4_supproutines, tcg_p2_structures}. Supported cryptographic algorithms are also subject to performance analysis where the time to execute such an algorithm is repeatedly measured and recorded. Additionally, the tool uses the TPM to generate key pairs for RSA and ECC-based algorithms so that they can be further analyzed by various means.
goI